### 2020-02-03 nlp_models.tex
updating nlp

Note that Figure \ref{fig:GPT-snorm-hist} also shows a couple unusually large Spectral Norms, but,
here, simply correspond to the change in normalization of the word embedding layer(s) and can be ignored.
From Figure \ref{fig:gpt-snorm-layer} (below), we see that these correspond to the first embedding layer(s).
These layers appear to have a different effectvie normalization, and therefore a different scale.
For example, in GPT, most layers, the maximum eigenvalue $\lambda_{max}\sim\mathcal{O}(10-100)$,
but in the first embedding layer, the maximum is of order N (the number of words in the embedding), or
 $\lambda_{max}\sim\mathcal{O}(10^{5})$.  For GPT and GPT2, we layer all layers as-is (although one may to normalize
the first 2 layers by  $\mathbf{X}$ by $\frac{1}{N}$, or to treat them as an outlier).
Here, we do not include them in our computed average metrics in Table \ref{table:nlp},
and do not include them in the histogram plot in Figure \ref{fig:GPT-snorm-hist}.

>>>>

Note that Figure \ref{fig:GPT-snorm-hist} also shows some unusually large Spectral Norms, but,
here, simply correspond to the change in normalization of the word embedding layer(s) and can be ignored.
From Figure \ref{fig:gpt-snorm-layer} (below), we see that these correspond to the first embedding layer(s).
These layers appear to have a different effectvie normalization, and therefore a different scale.
For example, in GPT, most layers, the maximum eigenvalue $\lambda_{max}\sim\mathcal{O}(10-100)$,
but in the first embedding layer, the maximum is of order N (the number of words in the embedding), or
 $\lambda_{max}\sim\mathcal{O}(10^{5})$.  For GPT and GPT2, we layer all layers as-is (although one may to normalize
the first 2 layers by  $\mathbf{X}$ by $\frac{1}{N}$, or to treat them as an outlier).
Here, we do not include them in our computed average metrics in Table \ref{table:nlp},
and do not include them in the histogram plot in Figure \ref{fig:GPT-snorm-hist}.
